Multimodal Corpora

### 2017-01-17 Slides/Slides.tex
finishes slides for SmartKom

	\section{BAS SmartKom Corpus}

>>>>

	\section{BAS SmartKom Corpus} 	
	\subsection{General Information}
			\begin{frame}{The BAS SmartKom Corpus}{General Information}			
				\begin{itemize}
					\item released in 2001
					\cite{basSKP}
					\item extended and finalized in 2003
					\item modalities:
					\begin{itemize}
						\item 10 Audio streams
						\item 4 Video streams
						\item annotations including gestures and emotions
					\end{itemize}
					\item part of the SmartKom projectu
				\end{itemize}											
			\end{frame}		
			\begin{frame}{The BAS SmartKom Corpus}{General Information}			
				\begin{itemize}
					\item collaborative work:
					\begin{itemize}
						\item Universities
						\begin{itemize}
							\item Munich
							\item Erlangen
							\item Stuttgart
						\end{itemize}
						\item Industrial partners
						\begin{itemize}
							\item Daimler/Chrysler
							\item DFKI
							\item European Media Lab
							\item Philips
							\item Media Interface
							\item Siemens
							\item SONY
						\end{itemize}
					\end{itemize}
				\end{itemize}											
			\end{frame}

		\subsection{Motivation}
			\begin{frame}{The BAS SmartKom Corpus}{Motivation}			
				\begin{itemize}
					\item exploring natural multi-modal Computer-User-Interfaces
					\item focus on laypeople and unsupervised usage
					\item large variance in tasks and environments
				\end{itemize}											
			\end{frame}

		\subsection{Recording Scenario}
			\begin{frame}{The BAS SmartKom Corpus}{Recording Scenario}																\begin{figure}
					\includegraphics[width=0.7\textwidth]{images/BAS/setup}
					\caption{The 'Public' Recording Setup}
					\vspace*{-10pt}
					\caption*{Source: \cite{basSKP}}
				\end{figure}
			\end{frame}

		\subsection{Recorded Data}
			\begin{frame}{The BAS SmartKom Corpus}{Primary Data}										
				\begin{itemize}
					\item Video of face, frontal and fixed position
					\item Video of the upper body, from the left, fixed
					\item Infrared Video of projected Interface for Hand tracking
					\item 10 Audio channels
					\begin{itemize}
						\item 4 element microphone array
						\item directed microphone
						\item headset and/or lapel microphone
						\item stereo background noise 
						\item system output
					\end{itemize}
					\item Graphical System output, low framerate
					\item Combined Stream of all 4 video streams
					\item Coordinates of finger tip or pencil position		
				\end{itemize}
			\end{frame}

		\begin{frame}{The BAS SmartKom Corpus}{Secondary Data}
			\begin{itemize}
				\item Transliteration of audio channel 
				\item Turn segmentation
				\item Segmentation and labeling of gestures in two dimensions
				\item Segmentation and labeling of user state
				\begin{itemize}
					\item using facial and speech information
					\item using only facial information 
				\end{itemize}
				\item Segmentation and labeling of prosodic features to recognize emotions
			\end{itemize}
		\end{frame}
		\begin{frame}{The BAS SmartKom Corpus}{Example Data}
		\begin{figure}
			\includegraphics[width=0.8\textwidth]{images/BAS/stream}
			\caption{Unified QuickTime stream}
			\vspace*{-10pt}
			\caption*{Source: \cite{basSKP}}	
			\end{figure}		
		\end{frame}

		\subsection{Application}
			\begin{frame}{The BAS SmartKom Corpus}{Application}
				\begin{itemize}
					\item audio-only subset used for emotion research (SKAUDIO)
					\item research into the properties of symmetric multi-modal Interfaces\cite{wahlster2003towards}
				\end{itemize}
			\end{frame}
